---
title: "Import YRBS to R"
author: "Maura Beaton"
date: '2022-07-16'
---

This file outlines the steps to import data from the Youth Risky Behaviors Survey (YRBS) into R. 

### Step 1

Download and install the `devtools` package, which will allow you to download additional packages from github.

```{r devtools, eval = FALSE}
# Install the devtools package
install.packages( "devtools" , repos = "http://cran.rstudio.com/" )
```

### Step 2

With the `devtools` package installed, you can now download and install the `lodown` package from github. 

```{r lodown, eval = FALSE}
# Install the lodown package
library(devtools)
install_github( "ajdamico/lodown" , dependencies = TRUE )
```

The `lodown` package is designed to download an import all YRBS data and microdata from the CDC website into R. 

### Step 3

With the `lodown` package installed, you are now able to download the YRBS dataset directly onto your computer. 

```{r download, eval = FALSE}
# Download the YRBS high school data from the CDC website
library(lodown)
lodown( "yrbss" , output_dir = file.path( path.expand( "~" ) , "YRBSS" ) )
```

### Step 4

With the files downloaded, you can import the compiled dataset, saved as *"2019 main.rds"*, into R. This compiled dataset includes YRBS data from all 50 US states and all years the survey was conducted.

```{r import, eval = FALSE}
# Import compiled YRBS dataset
yrbs_all <- readRDS( file.path( path.expand( "~" ) , "YRBSS" , "2019 main.rds" ) )

# Create a dataframe and tibble
yrbs_df <- data.frame(yrbss_all)
yrbs_df <- tibble(yrbss_df)
```

Following these steps, you should now have all YRBS data available as a data frame and tibble in your environment. If you've encountered any issues along the way, additional guidance is available here: <http://asdfree.com/youth-risk-behavior-surveillance-system-yrbss.html>